Epilepsy example

### 2022-11-17 src/epil/epil.Rmd
Add EB R-INLA versions

---
title: "Epilepsy example"
author:
- name: Adam Howes
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
bibliography: citations.bib
abstract: |
  **Background** @rue2009approximate use the epilespy example from the OpenBUGs manual as demonstration of the integrated nested Laplace approximation method.

@@

```{r}
epil_inla <- function(strat) {
  inla(formula,
       control.fixed = list(mean = 0, prec = 1 / 100^2), #' Beta prior
       family = "poisson",
       data = Epil,
       control.inla = list(strategy = strat),
       control.predictor = list(compute = TRUE))
}

fit2 <- epil_inla(strat = "gaussian")
fit3 <- epil_inla(strat = "simplified.laplace")
fit4 <- epil_inla(strat = "laplace")
```

@@

```{r results='hide'}
fit8 <- aghq::marginal_laplace_tmb(
  obj,
  k = 3,
  startingvalue = c(param$l_tau_epsilon, param$l_tau_nu)
)

fit8_samples <- aghq::sample_marginal(fit8, M = 1000)$samps %>%
  t() %>%
  as.data.frame() %>%
  inf.utils::replace_duplicate_colnames()
```

@@

```{r}
stan1 <- as.vector(t(summary(fit1)$summary[1:6, c(1, 3)]))
inla2 <- as.vector(t(fit2$summary.fixed[1:6, 1:2]))
inla3 <- as.vector(t(fit3$summary.fixed[1:6, 1:2]))
inla4 <- as.vector(t(fit4$summary.fixed[1:6, 1:2]))
tmb5 <- as.vector(t(data.frame(sd_out$par.random[1:6], sqrt(sd_out$diag.cov.random[1:6]))))
glmmtmb6 <- as.vector(t(summary(fit6)$coefficients$cond[, c("Estimate", "Std. Error")]))
tmbstan7 <- as.vector(t(summary(fit7)$summary[1:6, c(1, 3)]))

fit8_beta_samples <- fit8_samples[, 1:6]
aghq8 <- as.vector(t(data.frame(mean = apply(fit8_beta_samples, 2, mean), sd = apply(fit8_beta_samples, 2, sd))))

adam9 <- as.vector(t(laplace_beta_summary[1:6, 1:2]))

df <- cbind(stan1, inla2, inla3, inla4, tmb5, glmmtmb6, tmbstan7, aghq8, adam9) %>%
  as.data.frame() %>%
  mutate(type = gl(2, 1, 12, labels = c("Mean", "SD")))

beta_i <- function(i) { c(paste0("beta_", i), paste0("sd(beta_", i, ")")) }
rownames(df) <- c(sapply(0:5, beta_i))
colnames(df) <- c("Stan", "R-INLA_G", "R-INLA_SL", "R-INLA_L", "TMB", "glmmTMB", "tmbstan", "aghq", "adam", "type")

df %>%
  select(-type) %>%
  kableExtra::kable()

>>>>

---
title: "Epilepsy example"
author:
- name: Adam Howes
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
bibliography: citations.bib
abstract: |
  **Background** @rue2009approximate use the epilespy example from the OpenBUGs manual as demonstration of the integrated nested Laplace approximation method. The model is a Poisson GLMM including both fixed and random effects.

@@

```{r}
epil_inla <- function(strat, int_strat) {
  inla(formula,
       control.fixed = list(mean = 0, prec = 1 / 100^2), #' Beta prior
       family = "poisson",
       data = Epil,
       control.inla = list(strategy = strat, int.strategy = int_strat),
       control.predictor = list(compute = TRUE))
}

fit2 <- epil_inla(strat = "gaussian", int_strat = "eb")
fit3 <- epil_inla(strat = "simplified.laplace", int_strat = "eb")
fit4 <- epil_inla(strat = "laplace", int_strat = "eb")

fit5 <- epil_inla(strat = "gaussian", int_strat = "grid")
fit6 <- epil_inla(strat = "simplified.laplace", int_strat = "grid")
fit7 <- epil_inla(strat = "laplace", int_strat = "grid")
```

@@

```{r results='hide'}
fit11 <- aghq::marginal_laplace_tmb(
  obj,
  k = 3,
  startingvalue = c(param$l_tau_epsilon, param$l_tau_nu)
)

fit11_samples <- aghq::sample_marginal(fit8, M = 1000)$samps %>%
  t() %>%
  as.data.frame() %>%
  inf.utils::replace_duplicate_colnames()
```

@@

```{r}
stan1 <- as.vector(t(summary(fit1)$summary[1:6, c(1, 3)]))
inla2 <- as.vector(t(fit2$summary.fixed[1:6, 1:2]))
inla3 <- as.vector(t(fit3$summary.fixed[1:6, 1:2]))
inla4 <- as.vector(t(fit4$summary.fixed[1:6, 1:2]))
inla5 <- as.vector(t(fit2$summary.fixed[1:6, 1:2]))
inla6 <- as.vector(t(fit3$summary.fixed[1:6, 1:2]))
inla7 <- as.vector(t(fit4$summary.fixed[1:6, 1:2]))
tmb8 <- as.vector(t(data.frame(sd_out$par.random[1:6], sqrt(sd_out$diag.cov.random[1:6]))))
glmmtmb9 <- as.vector(t(summary(fit6)$coefficients$cond[, c("Estimate", "Std. Error")]))
tmbstan10 <- as.vector(t(summary(fit7)$summary[1:6, c(1, 3)]))

fit11_beta_samples <- fit8_samples[, 1:6]
aghq11 <- as.vector(t(data.frame(mean = apply(fit11_beta_samples, 2, mean), sd = apply(fit8_beta_samples, 2, sd))))

adam12 <- as.vector(t(laplace_beta_summary[1:6, 1:2]))

df <- cbind(stan1, inla2, inla3, inla4, inla5, inla6, inla7, tmb8, glmmtmb9, tmbstan10, aghq11, adam12) %>%
  as.data.frame() %>%
  mutate(type = gl(2, 1, 12, labels = c("Mean", "SD")))

beta_i <- function(i) { c(paste0("beta_", i), paste0("sd(beta_", i, ")")) }
rownames(df) <- c(sapply(0:5, beta_i))
colnames(df) <- c("Stan", "EB-G", "EB-SL", "EB-L", "Grid-G", "Grid-SL", "Grid-L", "TMB", "glmmTMB", "tmbstan", "aghq", "adam", "type")

df %>%
  select(-type) %>%
  kableExtra::kable(digits = 3)
